Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-05-10 appendix.tex
add a reply

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_EKRT.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_EKRT.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_EKRT.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
        \label{fig:Figure_8}
              \end{center}
\end{figure*}

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_VISH.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_VISH.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_VISH.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_9}
              \end{center}
\end{figure*}

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_9}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$. More specifically, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely fit $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. Compared with these two calculations, the calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3 and 4). Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ (n = 2 and 3),  50\% for $v_4$. The calculations with AMPT initial conditions describe the data better with the precision 10-20\%.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_AMPT.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_AMPT.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_AMPT.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
        \label{fig:Figure_10}
              \end{center}
\end{figure*}

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_modelcomparisonBest.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_modelcomparisonBest.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_modelcomparisonBest.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to few selected model calculations from three theoretical models which describe the $v_n$ data best.}
        \label{fig:Figure_11}
              \end{center}
\end{figure*}

>>>>

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_comp_EKRT.eps}}\hspace{-0.37cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_comp_EKRT.eps}}\hspace{-0.37cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_comp_EKRT.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
        \label{fig:Figure_8}
              \end{center}
\end{figure*}

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_comp_VISH.eps}}\hspace{-0.37cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_comp_VISH.eps}}\hspace{-0.37cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_comp_VISH.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_9}
              \end{center}
\end{figure*}

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_9}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$. In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely describe $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ (n = 2, 3 and 4). Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ (n = 2 and 3),  50\% for $v_4$. The calculations with AMPT initial conditions describe the data better with the precision 10-20\%.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_comp_AMPT.eps}}\hspace{-0.37cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_comp_AMPT.eps}}\hspace{-0.37cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_comp_AMPT.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
        \label{fig:Figure_10}
              \end{center}
\end{figure*}

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_modelcomparisonBest.eps}}\hspace{-0.37cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_modelcomparisonBest.eps}}\hspace{-0.37cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_modelcomparisonBest.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to few selected model calculations from three theoretical models which describe the $v_n$ data best.}
        \label{fig:Figure_11}
              \end{center}
\end{figure*}
